---
title: "Writing technical reports of any economic analysis in R with **bookdown**"
subtitle: "A short tutorial for *R for HTA* using a tutorial by Alvarez and Ribero"
author: "FW Thielen"
date: "`r Sys.Date()`"
subparagraph: true
output: 
  bookdown::pdf_book:
    extra_dependencies: ["float"]
    includes:
      in_header: preamble.tex
    toc: true
    toc_depth: 4
site: bookdown::bookdown_site
documentclass: report
fontsize: 12pt
geometry: "left=3cm, right=3cm, top=2.5cm, bottom=2.5cm"
bibliography: ["references/zotero.bib", "references/packages.bib"]
biblio-style: "numeric"
csl: [references/nature.csl]
link-citations: yes
Description: "DRAFT"
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}

# General R session settings
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE) # for all subsequent chunks
```

# Preface {-}

This book was created to demonstrate how the online "Tutorial to Create a
Discrete Event Simulation Model in R Using descem", written by *Javier Sanchez Alvarez*
and *Valerie Aponte Ribero* and published on [**R for HTA**](https://r-hta.org/tutorial/descem/) can be converted into a **bookdown**
report/book.[@bookdown2016]

This report, together with its code can be found on [github](https://github.com/fthielen/2022-r_for_hta) and was written for the
*R for HTA workshop* on Thursday 19th, Friday 20th, and Monday 23rd May 2022.
It is part of the presentation on Monday 23rd May 2022: "Copy and paste code,
not output. Writing technical reports of any economic analysis in R with Bookdown"
and "Estimating Dutch costs of productivity losses in R using up-to-date data
from Statistics Netherlands (CBS) with the R-package cbsodataR". More on
costs of producitivty losses can be found in Krol and Brouwer (2014).[@krol2014]

## Setup {-}
The following R-code chunk is only visible in the `index.Rmd` file, unless the
chunk option `echo` is set to `TRUE`.

This chunk also controls the options for all other chunks in the document. These
options can be overruled in each chunk separately.

Be aware that options like `warnings = FALSE` can be undesirable and should be
used with caution.

```{r chunk-opts, echo=FALSE, message=FALSE, warning=FALSE}

# General R session settings
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE) # for all subsequent chunks
```

## Other {-}

The standard approach of **bookdown** is to first merge all `.Rmd` files you
specified in the `_bookdown.yml` file. After that, these files are rendered.
Therefore, all object used in later chapter need to be created somewhere in a
previous one.

Rmarkdowns behave as they usually do:

- One `#` is for first level headings
- Two `##` is for second level headings, and so on
- A `{-}` after a heading means that it is not automatically numbered

You can render this book either:

- as a PDF file with: 
```{r eval-pdf, eval=F}
bookdown::render_book(here::here("scripts/Rmd/index.Rmd"),
                      output_format = "bookdown::pdf_book")
```
- or as a HTML file with:
```{r eval-html, eval=F}
bookdown::render_book(here::here("scripts/Rmd/index.Rmd"),
                      output_format = "bookdown::gitbook")
```

